The \dealii Library, Version 9.7

### 2025-08-07 9.7/paper.tex
List the major changes with links.

The major changes of this release are:
%
\begin{itemize}
\item
  \todo[inline]{Update list from the subsections of Section 2
    below. Like in the previous release papers, we here basically give
  a 1-3 sentence summary of the subsections 2.x, with a link to that section.}
\end{itemize}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The \texttt{MappingP1} class}

@@

\subsection{Matrix-free functionality}

>>>>

The major changes of this release are:
%
\begin{itemize}
\item
\todo[inline]{Keep this list of major changes up-to-date - the formatting is the
  same as the 9.6 paper.}

\item \texttt{MappingP1}, a more efficient mapping for simplex elements
  (Section~\ref{subsec:mappingp1})

\item Improved support for transfering solution vectors during mesh refinement
  (Section~\ref{subsec:solutiontransfer})

\item Improved matrix-free support for multi-component systems as well as
  improved portability between GPUs via \texttt{Portable::MatrixFree}
  (Section~\ref{subsec:matrixfree})

\item Improved support for threading via TaskFlow, as well as support for
  several new external libraries and improved support for Kokkos and ArborX
  (Section~\ref{subsec:external})

\item Support for C++20 modules (Section~\ref{subsec:modules})

\item Three new tutorial programs and a new code gallery program
  (Section~\ref{subsec:steps})
\end{itemize}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The \texttt{MappingP1} class}
\label{subsec:mappingp1}

@@

\subsection{Matrix-free functionality}
\label{subsec:matrixfree}
